---
Title   : "Quantmod"
Author  : "cms"
Date    : "February 11, 2019"
Output  : html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(quantmod)
library(PerformanceAnalytics)
library(RColorBrewer)
library(tseries)
library(lubridate)
library(Quandl)
Quandl.api_key("zrcB2Ejv9UmvhPCUsy2_")
options("getSymbols.yahoo.warning"=FALSE)
```

# Intro : We will load the libraries and capture some data for a stock and do a quick line graph

```{r}
MSFT <- getSymbols("MSFT", auto.assign = FALSE)
head(MSFT)
dim(MSFT)
```

# Our first task will be to download daily returns for a new Stock. We can start with amazon.

```{r}
new <- MSFT[1:30, 1:3]
MSFT["2007-01-03","MSFT.Open"]
```

# Let's look at the Head and Tail of the Df

```{r}
head(MSFT)
tail(MSFT)
dim(MSFT)
str(MSFT)
```

# In this task we're going to learn subsetting fundamentals. We can do it by row/column reference or by row/column name

```{r}
df <- as.data.frame(MSFT)
class(df)
head(df)
df <- as.xts(df)
class(df)

write.csv(df, "newdatamsft.csv")
read.csv(df, "newdatamsft")
```

# In this task  I am going to show you how to rename the columns or easier subsetting. I am also going to show you how to save data into .csv file for import into excel.

```{r}

```

# In this task we will learn about xts. zoo objects and how to convert back and forth between xts and data frames.

```{r}

```

# In this task we will create a Daily Return and then Chart the data for one stock.

```{r}
options(scipen = 9999)
tsla <- getSymbols("TSLA", auto.assign = F)
head(tsla, 20)
head(dailyReturn(tsla$TSLA.Adjusted))
plot(dailyReturn(tsla$TSLA.Adjusted), type = "l")
```

# Next project will consist of more data analytics and comparing multiple stocks againts each other.

```{r}
msft <- getSymbols("MSFT", auto.assign = F)
msft_Ad <- Ad(msft)
head(msft_Ad)
msft_daily <- dailyReturn(msft_Ad)
head(msft_daily)

new_msft <- dailyReturn(Ad(getSymbols("MSFT", auto.assign = F)))
head(new_msft)
```

```{r}
fb <- getSymbols("FB", auto.assign = F)
fb_ad <- Ad(fb)
fb_daily <- dailyReturn(fb_ad)

dim(fb_daily)

new_fb <- dailyReturn(Ad(getSymbols("FB", auto.assign = F)))

comb <- merge(new_msft, new_fb)
head(comb)
comb_traded <- merge(new_msft, new_fb, aall = F)

head(comb_traded)
dim(comb_traded)
```

