---
Title   : "Quantmod III"
Author  : "cms"
Date    : "9/4/2019"
Output  : html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(quantmod)
library(tidyverse)
```

# Pull down stock data for TSLA using Get Symbols

```{r}
tsla <- getSymbols("TSLA", auto.assign = F)
head(tsla)
```

# Store Closing Price (adjusted for stock splits)

```{r}
tsla_cl <- tsla$TSLA.Close
head(tsla_cl)
tsla_cl2 <- Ad(tsla)
head(tsla_cl2)
```

# What is lag

```{r}
?lag
head(Lag(tsla_cl, 2))
```


# Remove Scientific Notation

```{r}
options(scipen = 9999)
```

# Create daily % change vector

```{r}
daily_change <- tsla_cl/Lag(tsla_cl, 1) -1
head(daily_change)
```

# Look at histogram of percentage change

```{r}
hist(daily_change, 40, col = "magenta")
```

```{r}
buy_signal <- .04
```

# Loop Over all trading days (except the first)
buy_signal == parameter
tsla_cl == data
daily_change == %change
signal == 1 or 0 buy/sell

```{r}
signal <- c(NULL)
```

```{r}
for (i in 2:length(tsla_cl)) {
  if (daily_change[i] > buy_signal) {signal[i] <- 1}
  else {signal[i] <- 0}
}
head(signal, 40)
```

# Reclassify signal to an xts object (tying it to a date)

```{r}
signal <- reclass(signal, tsla_cl)
head(signal, 20)
```

# Chart the Series

```{r}
chartSeries(tsla_cl,
            type = "l",
            subset = "2011-01::2012-01",
            TA = c(addBBands(n = 20, sd = 2)),
            theme = chartTheme("black"))
?addTA
addTA(signal,
      type = 's',
      col = "red")
chartSeries(msft,
            subset = "2007",
            TA = c(addBBands(n = 20, sd = 2), addRSI(),
            addEMA(n = 30), addMACD()),
            theme = chartTheme("black"))
```

